Draft

### 2024-08-05 Draft/Draft.Rmd
Draft with plots

>>>>

## Plots ----------

```{r}
install.packages("ggplot2")
library(ggplot2)

# Setup the data
m <- matrix(c(8,3,4,1,5,9,6,7,2), nrow=3, ncol=3)
df <- expand.grid(x=1:ncol(m),y=1:nrow(m))
df$val <- m[as.matrix(df[c('y','x')])]

library(ggplot2)
library(scales)
test <- ggplot(df, aes(x=x, y=y, label=val)) + 
  geom_tile(fill='transparent', colour = 'black') + 
  geom_text(size = 14) + 
  scale_y_reverse() +
  theme_classic() + 
  theme(axis.text  = element_blank(),
        panel.grid = element_blank(),
        axis.line  = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank())

plot(test)
```

```{r}
# Create a data frame with the coordinates and colors
grid_data <- expand.grid(x = 1:10, y = 1:10)  # 10x10 grid
grid_data$color <- "white"  # Default color for all squares

# Specify the squares to be colored
colored_squares <- data.frame(
  x = c(2, 4, 6, 8),
  y = c(3, 5, 7, 9),
  color = c("red", "blue", "green", "yellow")
)

# Merge the colored squares into the grid data
grid_data <- merge(grid_data, colored_squares, by = c("x", "y"), all.x = TRUE)
grid_data$color.y[is.na(grid_data$color.y)] <- "white" # Set NA colors to white
# c(rep("white", 100))

ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
  geom_tile(colour = "black") +  # Draw the squares with black borders # 
  scale_fill_identity() +  # Use the colors specified in the data
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    axis.title = element_blank(),  # Remove axis titles
    axis.text = element_blank(),   # Remove axis text
    axis.ticks = element_blank(),  # Remove axis ticks
    panel.grid = element_blank()   # Remove grid lines
  ) +
  coord_fixed()  # Ensure squares are not stretched
```
